---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# libminer

<!-- badges: start -->
<!-- badges: end -->

The goal of libminer is to is to provide an overview of your R library setup. This is a toy package created as part of the Fundamentals of Package Development workshop given at Posit::conf(2023) 

## Installation

You can install the development version of libminer from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("franzenr/libminer")
```

## Example

To get a count of the total number of installed packages in each of your librarires, use `lib_summary()`. Including the optional `sizes = TRUE` argument will also return the size of each library. 

```{r example}
library(libminer)
## basic example code

lib_summary()
# specify sizes = TRUE
lib_summary(sizes = TRUE)
```
